Predicting Levels of Sales for Newly Published Books using Cost-Sensitive Ensemble Methods

### 2016-09-25 paper.tex
Fixed name of a figure
opened a section for methdology
Added description of setting up the experiments

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.50]{confusion-matrix}
\end{center}
\caption{Basic confusion matrix.}
\label{fig:confusionmatrix}
\end{figure*}

@@

>>>>

\section{Methodology}

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.50]{Confusion-matrix}
\end{center}
\caption{Basic confusion matrix.}
\label{fig:confusionmatrix}
\end{figure*}

@@

In all experiments, 10-folds cross validation methodology is applied for training and testing the developed classifiers. Moreover, in order to generate statistically reliable results, the 10-fold cross validation is repeated 10 times with different partitioning seeds then the average and standard deviation are calculated for each evaluation metric.

In the first stage of the experiments the basic classifiers k-NN, NB, MLP, J48 and SVM are applied for predicting the sales level. The performance of some classifiers is highly affected by the initial values of their parameters. For this reason, initial experiment were conducted to tune the parameters of k-NN, SVM and MLP. For k-NN the best classification results were obtained with k=1. For SVM, a rough grid search was used, the value for the cost $C$ is set to 50 and $\gamma$  to 0.01. For MLP, the number of hidden neurons is set to (number of features+ number of output classes)/2.
